Universal Anonymous Signatures

### 2022-07-19 prism-backend/research/gsac/relationships.tex
Applying comments by Markulf.
Done with main pass after Markulf's comments.

  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \textbf{Issuance functions:}
      \begin{align}
        & \fissue^1(\cdot,\cdot,\cdot) \coloneqq 1 \nonumber \\
        & \fissue^{\sring}(\usk,\attrs,\cdot) \coloneqq \pcif \attrs
          \subseteq \sring \cup \lbrace \CCommit(\usk;0) \rbrace: \pcreturn 1;
          \pcelse \pcreturn 0 \nonumber \\
        & \fissue^{l,\dattrs}(\usk,\attrs,(\cid,\cattrs)) \coloneqq
          \pcif \attrs_1 = l+1 \land \attrs \subseteq
          \lbrace \cattrs_i \rbrace_{i\in\dattrs}: \pcreturn 1;
          \pcelse \pcreturn 0 \nonumber
      \end{align}

      \textbf{Signature evaluation functions:}
      \begin{align}
        & \feval^0(\cdot,\cdot,\cdot) \coloneqq \pcreturn (0,\ast) \nonumber \\
        & \feval^{\dattrs}(\cdot,(\cid,\attrs),\cdot)
          \coloneqq \pcreturn (\lbrace \attrs_i \rbrace_{i\in \dattrs},\ast)
          \nonumber \\
        & \feval^{\sring}(\usk,(\cid,\attrs),\cdot)
          \coloneqq \pcif \CCommit(\usk;0) \in \attrs:
          \pcreturn (\attrs,\ast);
          \pcelse \pcreturn \bot \nonumber \\
        & \feval^{l,\dattrs}(\cdot,(\cid,\attrs),\cdot) \coloneqq
          \pcreturn((\attrs_1,\lbrace\attrs_i\rbrace_{i\in\dattrs}),\ast)
          \nonumber
      \end{align}
    \end{minipage}
  }
  \vspace*{1em}

  \scalebox{0.9}{
    \begin{minipage}[t]{0.5\textwidth}
      \textbf{Open functions:}
      \begin{align}
        & \finsp^0(\cdot,\cdot,\cdot,\cdot) \coloneqq 0 \nonumber \\
        & \finsp^{\upk}(\cdot,\usk,\cdot,\cdot) \coloneqq \CCommit(\usk;0)
          \nonumber
      \end{align}
    \end{minipage}
    \hspace*{5em}
    % \begin{minipage}[t]{0.47\textwidth}
    %   \begin{framed}
    %     $\attrs(\cred)$ returns all attributes in \cred \\
    %     $\dattrs(\cred)$ returns $\dattrs \subseteq \attrs(\cred)$ \\
    %     $\attrs_i(\cred)$ returns $i$-th attribute in \cred \\
    %     $\ast$ means the output is ignored \\
    %     $\bot$ means the function fails
    %   \end{framed}
    % \end{minipage}
  }
  \caption{Functions for the \CUASGen restrictions described next.
    For readability, we use ``$\cdot$'' to denote input arguments that are
    ignored; and ``$\ast$'' to denote output values that can be set to anything
    (but should be ignored). $\bot$ means the function fails.}
    % $\attrs(\cred)$ returns all attributes in \cred. $\dattrs(\cred)$ returns
    % $\dattrs \subseteq \attrs(\cred)$. $\attrs_i(\cred)$ returns $i$-th
    % attribute in \cred. $\ast$ means the output is ignored (in these examples,
    % we use this to mean that $\yeval^1$ is unused. $\bot$ means the function
    % fails.}
  \label{fig:func-restrictions}
\end{figure}

@@

We adopt the model in \cite{bsz05}. In this abstraction
of group signatures, the opener returns an index uniquely identifying the group
member that created a signature, along with a correctness proof. For ease of
exposition, assume that, w.l.o.g., this index is just the public key that the
group member chooses when joining the group\footnote{The user public key is
  assumed to be accessible from a public table in \cite{bsz05}, so it is direct
  to translate the public key into an index, if needed.}. A group signature
scheme, according to \cite{bsz05}, is composed of $KeyGen$, \UKeyGen, \Sign,
\Verify, \Open and \Judge algorithms, as well as an $\langle\Obtain,\Issue
\rangle$ interactive protocol. Their intuition is similar to that of
\UAS, so we refer to \cite{bsz05} for detailed descriptions. For ease of
reference, we replicate the security games in \figref{fig:model-gs}.

@@

\subsubsection{\CUASGS construction.} %
We show that the $(\fissue^1,\feval^0,\finsp^{\upk})$-\CUASGen restriction, is
a secure group signature scheme according to \cite{bsz05}. We first quickly
define the algorithms, and then prove security.

\begin{description}
\item[$(\gpk,\isk,\osk) \gets KeyGen(1^\secpar)$.] Runs the \Setup algorithm
  of \CUASGen, and one instance of \IKeyGen and \OKeyGen. Assigns the public
  keys to \gpk.
\item[$(\upk,\usk) \gets \UKeyGen(1^\secpar)$.] Runs \UKeyGen from \CUASGen, and
  computes $\CCommit(\usk;0)$ as \upk.
\item[$\langle \cred,\utrans \rangle \gets
  \langle\Obtain(\usk,\ipk),\Issue(\isk,\upk)\rangle$.] Runs $\langle\Obtain,
  \Issue\rangle$ as in \CUASGen, with $\attrs \gets \emptyset$. Note that, to
  constraint to only one credential per user, it suffices to require the user
  to prove that the ``randomness'' it uses when committing to its private key
  is actually $0$, and check whether the received commitment has been seen
  before.
\item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
  runs $(\sig,0) \gets \Sign(\usk,\opk,\cred,\msg,\feval^0)$ from \CUASGen.
  Simply returns \sig.
\item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
  returns whatever $\Verify(\opk,\ipk,\sig,0,\msg,\feval^0)$ from \CUASGen
  outputs.
\item[$(\upk,\pi) \gets \Open(\gpk,\osk,\trans,\sig,\msg)$.] Parses \gpk as
  $(\ipk,\opk)$, and returns whatever \CUASGen outputs in $\Open(\osk,\ipk,\sig,
  0,\msg,\feval^0)$. Internally, the call to \Open runs
  $\finsp^{\upk}$, where $\upk = \CCommit(\usk;0)$, just as proved in $\langle
  \Obtain,\Issue\rangle$.
\item[$1/0 \gets \Judge(\gpk,\pi,\upk,\sig,\msg)$.] Parses \gpk as $(\ipk,
  \opk)$, and returns whatever \CUASGen outputs in $\Judge(\opk,\upk,\pi,\sig,
  0,\msg)$.
\end{description}

@@

\begin{theorem}[Traceability of \CUASGS]
  If the base \CUASGen construction has unforgeable signing according to
  \defref{def:sign-forge-uas}, then \CUASGS is a traceable group signature
  scheme.
\end{theorem}

@@

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.55\textwidth}        
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,rs}(1^\secpar)$}{%
        ((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar) \\
        (i_0,i_1,R,\msg,\st) \gets \adv^{SIGN}(\pk_1,\dots,\pk_n) \\
        \pcif % R \not\subseteq \lbrace [n] \rbrace \lor
        \lbrace \pk_{i_0},\pk_{i_1} \rbrace \notin R \lor %\\
        i_0 = i_1: \pcreturn \bot \\
        \sig \gets Sign(\sk_{i_b},R,\msg)) \\
        b^* \gets \adv(\sig,\st) \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.5\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,rs}(1^\secpar)$}{%
        ((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar) \\
        (R,\sig,\msg) \gets \adv^{SIGN,CORR}(\pk_1,\dots,\pk_n) \\
        \pcif Verify(R,\sig,\msg) = 0: \pcreturn 0 \\
        \pcreturn 1~\pcif R \subseteq [n] \setminus CU = \emptyset~\land \\
        \pcind \adv~\textrm{never queried}~SIGN(\cdot,R,\msg) \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for ring signatures \cite{bkm06}. The SIGN oracle
    accepts a $(i,R,\msg)$ tuple, with $pk_i \in R$, and
    returns $\sig \gets Sign(\sk_i,R,\msg)$. The oracle $CORR$ accepts an
    index $i$, and leaks $\sk_i$ to $\adv$. Corrupted user indexes are
    added to $CU$.}
  \label{fig:model-rs}  
\end{figure}

\subsubsection{\CUASRing Construction.} %
We first define in \eref{eq:sign-prv} an alternative NP relation for signing,
$\NIZKRel_{\Sign}^{prv}$, which we use to replace $\NIZKRel_{\Sign}$ in \CUASGen.
It is essentially the same, except that the issuer public key is kept private,
and we add an extra check for proving that the issuer public key is one of the
keys in the ring. We refer to the resulting \CUASGen construction as
$\CUASGen^{\Sign-prv}$. Since, in the following syntax, we limit to one
credential per signature, it is easy to see that the modified relation for
signing does not affect security.

\begin{align}
  & \NIZKRel_{\Sign}^{prv} \coloneqq \lbrace (\usk,\cred,\yeval^1,\yinsp,r,r',
    \ipk),(\msg,\feval,\yeval^0,\ceval,\cinsp,\Eek,\widetilde{\Eek},\sring): \nonumber \\
  & \hspace*{6.405em}\ceval = \EEnc(\widetilde{\Eek},\yeval^1;r) \land
    \cinsp = \EEnc(\Eek,\yinsp;r') \land \nonumber \\
  & \hspace*{6.40em}(\yeval^0,\yeval^1) = \feval(\usk,\cred,\msg) \land
    \yinsp = \finsp((\yeval^0,\yeval^1),\usk,\cred,\msg) \nonumber \\
  & \hspace*{6.40em}\exists \ipk \in \sring~\suchthat~\SBCMVerify(\ipk,\cred,\usk,
    \sring) = 1) \rbrace \label{eq:sign-prv}
\end{align}

From it, we show that the $(\fissue^{\sring},\feval^{\attrs},\finsp^0)$-
$\CUASGen^{\Sign-prv}$ restriction, is a secure ring signature scheme. We
restrict to one credential per signature.

\begin{description}  
\item[$\parm \gets \Setup(\secpar,\AttrSpace)$.] As in $\CUASGen^{\Sign-prv}$.  
\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.] As in
  $\CUASGen^{\Sign-prv}$, using $\fissue^{\sring}$.  
\item[$(\opk,\osk) \gets \OKeyGen(\parm,\finsp).$] As in $\CUASGen^{\Sign-prv}$,
  restricting \finsp to be $\finsp^0$.  
\item[$\usk \gets \UKeyGen(\parm).$] Can only be run after \IKeyGen. Let 
  $\usk \gets \isk$. Note that this does not affect security, as long as
  $\isk \getr \AttrSpace$.
\item[$\langle \cred,\bot,\utrans,\bot \rangle \gets
  \langle \Obtain(\usk,\scred,\attrs),\Issue(\isk,\sipk,\attrs)\rangle.$]
  The user picks a set of public keys from a publicly available list of issuers
  (users), i.e. $\sring \gets \lbrace \ipk_i \rbrace_{i \in [t]}$, for some $t$.
  Then, runs the $\langle \Obtain,\Issue \rangle$ protocol as in
  $\CUASGen^{\Sign-prv}$, acting both as user and as issuer, using
  $\fissue^{\sring}$ as issuance function, and $\attrs \gets \sring$.
\item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\cred,\msg,\feval).$] As in
  $\CUASGen^{\Sign-prv}$, using $\feval^{\sring}$ as sign evaluation function,
  using as credential for signing the credential obtained in the desired
  $\langle \Obtain,\Issue \rangle$ session and, as \opk, any previously
  registered \opk (i.e., such that $\finsp=\finsp^0$).
\item[$1/0 \gets \Verify(\opk,\sring,\sig,\yeval,\msg,\feval).$] As in
  $\CUASGen^{\Sign-prv}$. Note that $\feval=\feval^{\attrs}$.
\item[$\Open$ and $\Judge$.] As in $\CUASGen^{\Sign-prv}$. Note that
  $\finsp=\finsp^0$.
\end{description}

@@

We adopt the model in \cite{fhs19}, for anonymous credentials with selective
disclosure. Therein, an anonymous credential scheme is
defined via $OrgKeyGen$ (which we rename to $IssKeyGen$), and $UserKeyGen$
algorithms (roughly equivalent to
\IKeyGen and \UKeyGen for \UAS), and $Obtain,Issue$ and $Show,Verify$
interactive protocols. The issuance interactive protocol is equivalent to
the issuance protocol in \UAS. Similarly, $Show,Verify$ is equivalent to
the interactive extension of \Sign and \Verify in \UAS, which we show how
to build in \appref{app:interactive-uas}. The security definitions rely on
$HU, CU, ObtIss, Obtain, Issue,Show$, and $LoR$ oracles, which are essentially
equivalent to our \HUGEN, \CUGEN, \OBTISS, \OBTAIN, \ISSUE, \SIGN, and \CHALb
oracles. We refer to \cite{fhs19} for the full details. For ease of reference,
we summarize the security definitions in \figref{fig:model-ac}, with inocuous
adaptations to make them more suitable for comparison with our definitions.

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.5\textwidth}        
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,ac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
        b^* \gets \adv^{HU,CU,Obtain,Show,LoR}(\isk) \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.5\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,ac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
        (D,\st) \gets \adv^{HU,CU,ObtIss,Issue,Show}(\ipk) \\
        \langle \cdot,(b,\utrans) \rangle
        \gets \langle \adv(\st),\Verify(\ipk,D) \rangle \\
        \pcif b = 1 \land \nexists j~\suchthat~(\OWNR[j] \in \CU
        \land D \subseteq \ATTR[j]): \\% \forall j, \OWNR[j] \in \CU
        % \implies D \not\subseteq \ATTR[j]: \\
        \pcind \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for anonymous credentials with selective disclosure
    \cite{fhs19}. \OWNR and \ATTR tables are essentially as in
    \secref{ssec:model-uas}.}
  \label{fig:model-ac}  
\end{figure}

\subsubsection{\CUASAC Construction.} %
We show that a $(\fissue^1,\feval^{\dattrs},\finsp^0)$-\CUASGen restriction, is
a secure anonymous credential scheme according to the model in \cite{fhs19}. We
first quickly define the algorithms, and then prove security. For better
alignment with \UAS, we add a common setup process which is part of $IssKeyGen$
in \cite{fhs19}. The change is inocuous functionality- and security-wise.

\begin{description}
\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\parm' \gets \Setup(1^\secpar,
  \AttrSpace)$ and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our
  \CUASGen construction. Returns $\parm \gets (\parm',\opk)$.
\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \IKeyGen from our
  \CUASGen construction, setting $\fissue^1$ as issuance function.
\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \UKeyGen from the
  \CUASGen construction, and computes $\CCommit(\usk;0)$ as \upk.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
  $\fissue^1$ as issuance function.
\item[$\langle 1/0,((1,\utrans)/(0,\utrans)\rangle
  \gets \langle Show(\ipk,\attrs,\dattrs,
  \cred),\Verify(\ipk,\dattrs) \rangle$.]
  Runs the interactive extension of \Sign and \Verify of the \CUASGen protocol,
  using $\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as
  open function, with \opk from \parm as opener public key.
\end{description}

@@

\begin{theorem}[Unforgeability of \CUASAC]
  \label{thm:forge-cuasac}
  If the base \CUASGen construction has signature unforgeability according to
  \defref{def:sign-forge-uas}, then \CUASAC is an unforgeable AC scheme.
\end{theorem}

>>>>

  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \textbf{Issuance functions:}
      \begin{align}
        & \fissue^1(\cdot,\cdot,\cdot) \coloneqq 1 \nonumber \\
        & \fissue^{single,L}((\upk,\cdot),\cdot,\cdot) \coloneqq
          \pcreturn \upk \notin L
          \nonumber \\
        & \fissue^{\sring}((\upk,\cdot),\attrs,\cdot) \coloneqq
          \pcreturn (\attrs \subseteq \sring \land \upk \in \sring) \nonumber \\
        & \fissue^{l,\dattrs}(\cdot,\attrs,(\cid,\cattrs)) \coloneqq
          \pcreturn (\attrs_1 = l+1 \land \attrs \subseteq
          \lbrace \cattrs_i \rbrace_{i\in\dattrs}) \nonumber
      \end{align}

      \textbf{Signature evaluation functions:}
      \begin{align}
        & \feval^0(\cdot,\cdot,\cdot) \coloneqq \pcreturn (0,\ast) \nonumber \\
        & \feval^{\dattrs}(\cdot,(\cid,\attrs),\cdot)
          \coloneqq \pcreturn (\lbrace \attrs_i \rbrace_{i\in \dattrs},\ast)
          \nonumber \\
        & \feval^{\sring}((\upk,\cdot),(\cid,\attrs),\cdot)
          \coloneqq \pcif \upk \in \attrs:
          \pcreturn (\attrs,\ast);
          \pcelse \pcreturn \bot \nonumber \\
        & \feval^{l,\dattrs}(\cdot,(\cid,\attrs),\cdot) \coloneqq
          \pcreturn((\attrs_1,\lbrace\attrs_i\rbrace_{i\in\dattrs}),\ast)
          \nonumber
      \end{align}
    \end{minipage}
  }
  \vspace*{1em}

  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \textbf{Open functions:}
      \begin{align}
        & \finsp^0(\cdot,\cdot,\cdot,\cdot) \coloneqq 0 \nonumber \\
        & \finsp^{\upk}(\cdot,(\upk,\cdot),\cdot,\cdot) \coloneqq
          \pcreturn \upk % \CCommit(\usk;0)
          \nonumber
      \end{align}
    \end{minipage}
    \hspace*{5em}
    % \begin{minipage}[t]{0.47\textwidth}
    %   \begin{framed}
    %     $\attrs(\cred)$ returns all attributes in \cred \\
    %     $\dattrs(\cred)$ returns $\dattrs \subseteq \attrs(\cred)$ \\
    %     $\attrs_i(\cred)$ returns $i$-th attribute in \cred \\
    %     $\ast$ means the output is ignored \\
    %     $\bot$ means the function fails
    %   \end{framed}
    % \end{minipage}
  }
  \caption{Functions for the \CUASGen restrictions described next.
    For readability, we use ``$\cdot$'' to denote input arguments that are
    ignored; and ``$\ast$'' to denote output values that can be set to anything
    (but should be ignored). $\bot$ means the function fails.}
    % $\attrs(\cred)$ returns all attributes in \cred. $\dattrs(\cred)$ returns
    % $\dattrs \subseteq \attrs(\cred)$. $\attrs_i(\cred)$ returns $i$-th
    % attribute in \cred. $\ast$ means the output is ignored (in these examples,
    % we use this to mean that $\yeval^1$ is unused. $\bot$ means the function
    % fails.}
  \label{fig:func-restrictions}
\end{figure}

@@

We adopt the model in \cite{bsz05}. In this abstraction
of group signatures, the opener returns an index uniquely identifying the group
member that created a signature, along with a correctness proof. For ease of
exposition, assume that, w.l.o.g., this index is just the public key that the
group member chooses\markulf{can he choose an existing public key?} when joining the group\footnote{The user public key is
  assumed to be accessible from a public table in \cite{bsz05}, so it is easy
  to translate the public key into an index, if needed.}. A group signature
scheme, according to \cite{bsz05}, is composed of $KeyGen$, \UKeyGen, \Sign,
\Verify, \Open and \Judge algorithms, as well as an $\langle\Obtain,\Issue
\rangle$ interactive protocol. Their intuition is similar to that of
\UAS, so we refer to \cite{bsz05} for detailed descriptions. For ease of
reference, we replicate the security games in \figref{fig:model-gs}.

@@

\subsubsection{\CUASGS construction.} %
We show that the $(\fissue^{single,L},\feval^0,\finsp^{\upk})$-\CUASGen
restriction, is a secure group signature scheme according to \cite{bsz05}.
Observe that the $\fissue^{single,L}$ function is further parameterized with
a list $L$ maintained by the issuer and must be fetched by users prior to
joining. It restricts that any user can have at most one credential (associated
to a same user key pair). We first quickly define the algorithms, and then
prove security.

\begin{description}
\item[$(\gpk,\isk,\osk) \gets KeyGen(1^\secpar)$.] Runs the \Setup algorithm
  of \CUASGen, and one instance of \IKeyGen and \OKeyGen. Assigns the public
  keys to \gpk.
\item[$(\upk,\usk) \gets \UKeyGen(1^\secpar)$.] Runs \UKeyGen from \CUASGen.
\item[$\langle \cred,\utrans \rangle \gets
  \langle\Obtain(\usk,\ipk),\Issue(\isk,\upk)\rangle$.] Runs $\langle\Obtain,
  \Issue\rangle$ as in \CUASGen, with $\attrs \gets \emptyset$.
\item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
  runs $(\sig,0) \gets \Sign(\usk,\opk,\cred,\msg,\feval^0)$ from \CUASGen --
  note that $0$ is the constant output of $\feval^0$.
\item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
  returns whatever $\Verify(\opk,\ipk,\sig,0,\msg,\feval^0)$ from \CUASGen
  outputs.
\item[$(\upk,\pi) \gets \Open(\gpk,\osk,\trans,\sig,\msg)$.] Parses \gpk as
  $(\ipk,\opk)$, and returns whatever \CUASGen outputs in $\Open(\osk,\ipk,\sig,
  0,\msg,\feval^0)$. Internally, the call to \Open runs $\finsp^{\upk}$.
\item[$1/0 \gets \Judge(\gpk,\pi,\upk,\sig,\msg)$.] Parses \gpk as $(\ipk,
  \opk)$, and returns whatever \CUASGen outputs in $\Judge(\opk,\upk,\pi,\sig,
  0,\msg)$.
\end{description}

@@

\begin{theorem}[Traceability of \CUASGS]
  If the base \CUASGen construction has unforgeable signing according to
  \defref{def:sign-forge-uas}, then \CUASGS is a traceable group signature
  scheme.\markulf{Hiding of $Com(\usk;0)$?}
\end{theorem}

@@

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.55\textwidth}        
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,rs}(1^\secpar)$}{%
        ((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar) \\
        (i_0,i_1,R,\msg,\st) \gets \adv^{SIGN}(\pk_1,\dots,\pk_n) \\
        \pcif R \not\subseteq \lbrace \pk_i \rbrace_{i\in[n]} \lor
        \lbrace \pk_{i_0},\pk_{i_1} \rbrace \not\subseteq R~\lor \\ %\\
        \pcind i_0 = i_1: \pcreturn \bot \\
        \sig \gets Sign(\sk_{i_b},R,\msg) \\
        b^* \gets \adv(\sig,\st) \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.5\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,rs}(1^\secpar)$}{%
        ((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar) \\
        (R,\sig,\msg) \gets \adv^{SIGN,CORR}(\pk_1,\dots,\pk_n) \\
        \pcif Verify(R,\sig,\msg) = 0: \pcreturn 0 \\
        \pcreturn (R \subseteq \lbrace \pk_i \rbrace_{i\in[n]} \setminus
        CU~\land \\
        \pcind \adv~\textrm{never queried}~SIGN(\cdot,R,\msg))
      }       
    \end{minipage}      
  }
  \caption{Security games for ring signatures \cite{bkm06}. The $SIGN$ oracle
    accepts $(i,R,\msg)$ tuples, with $pk_i \in R$, adds the tuple to a list of
    queries, and returns $\sig \gets Sign(\sk_i,R,\msg)$. $CORR$
    accepts an index $i$, and leaks $\sk_i$ to $\adv$. Corrupted users are added
    to $CU$.}
  \label{fig:model-rs}  
\end{figure}

\subsubsection{\CUASRing Construction.} %
Building a ring signature scheme according to the model in \figref{fig:model-rs}
is essentially a $(\fissue^{\sring},\feval^{\sring},\finsp^0)$-restriction of
our $\CUASGen^{hide-iss}$ construction. Concretely, for any desired ring, the
signer (who is also the issuer) simply must set $\sipk=\sring$. The construction
is as follows:

% \begin{align}
%   & \NIZKRel_{\Sign}^{prv} \coloneqq \lbrace (\usk,\cred,\yeval^1,\yinsp,r,r',
%     \ipk),(\msg,\feval,\yeval^0,\ceval,\cinsp,\Eek,\widetilde{\Eek},\sring): \nonumber \\
%   & \hspace*{6.405em}\ceval = \EEnc(\widetilde{\Eek},\yeval^1;r) \land
%     \cinsp = \EEnc(\Eek,\yinsp;r') \land \nonumber \\
%   & \hspace*{6.40em}(\yeval^0,\yeval^1) = \feval(\usk,\cred,\msg) \land
%     \yinsp = \finsp((\yeval^0,\yeval^1),\usk,\cred,\msg) \nonumber \\
%   & \hspace*{6.40em}\exists \ipk \in \sring~\suchthat~\SBCMVerify(\ipk,\cred,\usk,
%     \sring) = 1) \rbrace \label{eq:sign-prv}
% \end{align}

% From it, we show that the $(\fissue^{\sring},\feval^{\attrs},\finsp^0)$-
% $\CUASGen^{\Sign-prv}$ restriction, is a secure ring signature scheme. We
% restrict to one credential per signature.

\begin{description}
%\item[$\parm \gets \Setup(\secpar,\AttrSpace)$.] As in $\CUASGen^{hide-iss}$.
\item[$((\pk_1,\sk_1),...,(\pk_n,\sk_n)) \gets KeyGen(\secpar)$.] Runs
  $\parm \gets \Setup(\secpar)$ from $\CUASGen^{hide-iss}$, as well as $n$
  instances of $(\ipk_i,\isk_i) \gets \IKeyGen(\parm,\fissue^{\sring})$, and
  $(\opk,\osk) \gets \OKeyGen(\parm,\finsp^0)$.
  \jesus{This syntax restricts to fixing the rings at setup time. But the
    RS syntax in \cite{bkm06} is also somehow static already, in that it does
    not allow adding users on the fly. Is it ok?}
\item[$\langle \cred,\bot,\utrans,\bot \rangle \gets
  \langle \Obtain(\usk,\scred,\attrs),\Issue(\isk,\sipk,\attrs)\rangle.$]
  A user, with $\usk=\isk_i$ and $\upk=\ipk_i$ for some $i \in [n]$, self-issues
  to itself a credential for the ring \sring chosen at setup time. Then, runs
  the $\langle \Obtain,\Issue \rangle$ protocol as in $\CUASGen^{hide-iss}$,
  acting both as user and as issuer, using $\fissue^{\sring}$ as issuance
  function, and $\attrs \gets \sring$.
\item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\cred,\msg,\feval).$] As in
  $\CUASGen^{hide-iss}$, using $\feval^{\sring}$ as sign evaluation function,
  using as signing credential the self-issued credential.
\item[$1/0 \gets \Verify(\opk,\sipk,\sig,\yeval,\msg,\feval).$] As in
  $\CUASGen^{hide-iss}$. Note that $\sipk=\sring$, and $\feval=\feval^{\sring}$.
% \item[$\Open$ and $\Judge$.] As in $\CUASGen^{\Sign-prv}$. Note that
%   $\finsp=\finsp^0$.
\end{description}

@@

We adopt the model in \cite{fhs19}, for anonymous credentials with selective
disclosure. Therein, an anonymous credential scheme is
defined via $OrgKeyGen$ (which we rename to $IssKeyGen$), and $UserKeyGen$
algorithms (roughly equivalent to
\IKeyGen and \UKeyGen for \UAS), and $Obtain,Issue$ and $Show,Verify$
interactive protocols. The issuance interactive protocol corresponds to
the issuance protocol in \UAS. Similarly, $Show,Verify$ corresponds to
the interactive extension of \Sign and \Verify in \UAS, which we show how
to build in \appref{app:interactive-uas}. The security definitions rely on
$HU, CU, ObtIss, Obtain, Issue,Show$, and $LoR$ oracles, which are essentially
equivalent to our \HUGEN, \CUGEN, \OBTISS, \OBTAIN, \ISSUE, \SIGN, and \CHALb
oracles. We refer to \cite{fhs19} for the full details. For ease of reference,
we summarize the security definitions in \figref{fig:model-ac}.% , with inocuous
% adaptations to make them more suitable for comparison with our definitions --
% namely, we explicitly add a common setup process which is part of $IssKeyGen$
% in \cite{fhs19}.

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.5\textwidth}        
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,ac}(1^\secpar)$}{%
 %       \parm \gets \Setup(1^\secpar) \\
        (\ipk,\isk) \gets IssKeyGen(1^\secpar) \\        
        b^* \gets \adv^{HU,CU,Obtain,Show,LoR}(\isk) \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.5\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,ac}(1^\secpar)$}{%
%        \parm \gets \Setup(1^\secpar) \\
        (\ipk,\isk) \gets IssKeyGen(1^\secpar) \\        
        (D,\st) \gets \adv^{HU,CU,ObtIss,Issue,Show}(\ipk) \\
        \langle \cdot,(b,\utrans) \rangle
        \gets \langle \adv(\st),\Verify(\ipk,D) \rangle \\
        \pcreturn (b = 1 \land \nexists j~\suchthat \\
        \pcind (\OWNR[j] \in \CU
        \land D \subseteq \ATTR[j])) % \forall j, \OWNR[j] \in \CU
        % \implies D \not\subseteq \ATTR[j]: \\
        %\pcind \pcreturn 1 \\
        %\pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for anonymous credentials with selective disclosure
    \cite{fhs19}. \OWNR and \ATTR tables are essentially as in \UAS. \adv~wins
    the unforgeability game if it authenticates successfully while revealing
    attributes not contained in adversarially controlled credentials.}
  \label{fig:model-ac}  
\end{figure}

\subsubsection{\CUASAC Construction.} %
We show that a $(\fissue^1,\feval^{\dattrs},\finsp^0)$-\CUASGen restriction, is
a secure anonymous credential scheme according to the model in \cite{fhs19}. We
first quickly define the algorithms, and then prove security.

\begin{description}
% \item[$\parm \gets \Setup(1^\secpar)$.] Runs $\parm' \gets \Setup(1^\secpar,
%   \AttrSpace)$ and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our
%   \CUASGen construction. Returns $\parm \gets (\parm',\opk)$.
\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] $\parm' \gets
  \Setup(1^\secpar)$ and $(\opk,\osk) \gets \OKeyGen(\parm',
  \finsp^0)$ from \CUASGen, and sets $\parm \gets (\parm',\opk)$. Then,
  runs \IKeyGen, also from \CUASGen, setting $\fissue^1$ as issuance function.
\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \UKeyGen from \CUASGen.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
  $\fissue^1$ as issuance function.
\item[$\langle 1/0,((1,\utrans)/(0,\utrans)\rangle
  \gets \langle Show(\ipk,\attrs,\dattrs,
  \cred),\Verify(\ipk,\dattrs) \rangle$.]
  Runs the interactive extension of \Sign and \Verify of the \CUASGen protocol,
  using $\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as
  open function, with \opk from \parm as opener public key.
\end{description}

@@

\begin{theorem}[Unforgeability of \CUASAC]
  \label{thm:forge-cuasac}
  If the base \CUASGen construction has signature unforgeability according to
  \defref{def:sign-forge-uas}, then \CUASAC is an unforgeable AC scheme.
  \markulf{Hiding of $pk_U$?}
\end{theorem}
